# *Read a csv file*

## Read csv files in csv folder

```{r}
google <- read.csv("csv/googleplaystore.csv", sep = ",")
cars <- read.csv("csv/Auto.csv", sep = ",")

View(google)
View(cars)
```

## Read csv file through url

```{r}
url <- "https://github.com/rudeboybert/fivethirtyeight/blob/master/data-raw/congress-age/congress-terms.csv"
congress <- read.csv(url)
View(congress)
```

## Get access to a particular column

Using array

```{r}
google[, 3]
```

Or by typing the name of the column

```{r}
google$Rating
```

```{r}
unique(google$Rating)
```

# ***Calculation***

## Adding Up

```{r}
# Sum up the particular elements
sum(google$Rating[1], google$Rating[2], google$Rating[3])
```

```{r}
# We cannot sum it up directly because NaN exists.
sum(google$Rating)
```

```{r}
# We can type "na.rm = TRUE" to ignore NaN elements.
sum(google$Rating, na.rm = TRUE)
```

```{r}
sum(cars$horsepower, na.rm = TRUE)
```

There is a "?" in the column. We should replace it.

```{r}
cars$horsepower <- gsub("\\?", NA, cars$horsepower)
# Using as.numeric() to change the elments to numbers
sum(as.numeric(cars$horsepower), na.rm = TRUE)
```

## **Simple Calculations**

### **Add**

```{r}
sum(as.numeric(cars$horsepower), na.rm = TRUE)
```

### **Mean value**

```{r}
mean(as.numeric(cars$horsepower), na.rm = TRUE)
```

### **Median**

```{r}
median(as.numeric(cars$horsepower), na.rm = TRUE)
```

### **Maximum and Minimum**

```{r}
max(as.numeric(cars$horsepower), na.rm = TRUE)
min(as.numeric(cars$horsepower), na.rm = TRUE)
range(as.numeric(cars$horsepower), na.rm = TRUE)
```

### **Standard Deviation and Variance**

```{r}
sd(google$Rating, na.rm = TRUE)
var(google$Rating, na.rm = TRUE)
```

### **Length (within and without NaN)**

```{r}
length(google$Rating)

# Count the number of the elements which are not NaN.
length(google$Rating[!is.na(google$Rating)])

# Count the number of the elements which are NaN.
length(google$Rating[is.na(google$Rating)])
```

### **Sort and Order**

```{r}
# Sort the values.
sort(as.numeric(cars$horsepower))
sort(as.numeric(cars$horsepower), decreasing = TRUE)

# Present the order.
order(as.numeric(cars$horsepower))
```

### **Quantile**

```{r}
quantile(as.numeric(cars$horsepower), na.rm = TRUE)
```

# *Factor*

factor is one-dimensional

```{r}
yearFactor <- factor(cars$year, exclude = NA)
levels(yearFactor)
```
